Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-10-26 psy_peds_3.Rmd
add one additional output

# add the site id as column for each of the output data frames
count_icd$siteid = site 
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site 
table1$siteid = site

save( count_icd,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      table1,
      length_hospitalisation_values,
      file = paste0("output/peds_psy_aggResults_", site, ".RData"))
```

>>>>

# add the site id as column for each of the output data frames
count_icd$siteid = site 
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site 
table1$siteid = site 
ratios_patients_with_without_psy$siteid = site

save( count_icd,
      ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      table1,
      length_hospitalisation_values,
      file = paste0("output/peds_psy_aggResults_", site, ".RData"))
```
